Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-05-09 paper.tex

Four experiments have been conducted to evaluate the performance of our 
predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
Results will be evaluated on the complete datasets and specifically on the files that
do not behave consistently across subjects (\todo{explain this in introduction}).

We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
\[
        Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
\]
\[
        Sensitivity = \frac{TP}{TP+FN}
\]
\[
        Specificity = \frac{TN}{TN+FP}
\]
Where TP is the number of True Positives (correctly predicted errors), 
FP is the number of False Positives, TN is the number of true negatives 
and FN is the number of false negatives.

@@

\subsubsection{Random Unreal}
This method has a great performance with absolute accuracy of more than $0.95$ 
even by accessing to small training size of 10 percent. As it mentioned earlier 
this method is not applicable in pipline due to timestamp consideration but it 
is a good criteria to estimate the performance of other methods and try to modify 
the proposed methods in order to their accuracy be as closed as possible to the 
Random Unreal method ones.

\subsubsection{Complete Columns}
The Complete Columns method has
almost a constant accuracy even if the training ratio increased and it
is almost two times less than dummy classifier in more differentiated
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
best case which it means in similar conditions the Complete Columns
accuracy is as much accurate as the Dummy classifier which is $0.65$
percent.
\\
\subsubsection{Complete Rows}
This method has some 
flactuation over the gowth of training set size. These falactuations are more 
frequent in condition pairs which have higher difference positive ratio. 
Also by enlarging the training ratio specially between $0.3$ to $0.7$, 
we can see dummy classifier has better results than Complete Rows ones. 
In other words despite of better performance of Complete Rows than 
dummy classifier at the last 10 percent of the graph, its accuracies 
are less than dummy classifiers ones.  
\\
\subsubsection{Random Subjects-RS}
Same to the Complete Row method, RS method has some flactuation but not as frequent 
as Complete Rows method. Althogh there are some up and down trends specialy with 
training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
The method can be $0.99$ percent accurate when it has over 70 percent of the data however 
this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  
\\
\\
\noindent Figure~\ref{fig:ALS-Succeed} represents
the accuracy graph of all Random kind methods with comparision to dummy
classifier over the increasement of the training ratio.\\
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-6vs7}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:ALS-Succeed}
\end{figure}
\subsubsection{Random File Numbers(Uniform) - RFNU}
The continuous rise of RFNU accuracy trend can be observed in Figure~\ref{fig:ALS-Succeed}.
However a 0.03 drop is recorded in C6C7 between training ratio size of $0.8$ to $0.9$. 
This method takes over the dummy accuracy after having a training size more than 40 percent 
in condition pairs of C5vsC7 and C6vsC7 but it always shows better acuracy than 
dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).

% ALS-RFNT approaches
As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.

\subsubsection{RFNT-L}
In Figure~\ref{fig:ALS-Succeed}, the results show that RFNT-L performance is always more accurate than
dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
Dispite of this sudden mentioned drop to $78\%$ accuracy, RFNT-L method has slight growing trend throughout the 
increment of training ratio and its accuracy is always more than $90\%$.

@@

\subsection{Adding biases}
In this phase of experiment, the variation in values of utility matrix which caused by subjects and files are also considered. 
Figure~\ref{fig:ALS-Bias-PFS} presents the result of three methods of RFNU, RFNT-L and RFNT-S with having a comparison with
Random Unreal method.

@@

>>>>

Four experiments have been conducted to evaluate the performance of our 
predictions using (1) ALS without biases, (2) ALS with biases, (3) Biases only. 
Results will be evaluated on the complete datasets and specifically on the files that
do not behave consistently across subjects (\todo{explain this in introduction}).
\todo{the last sentence just applies for Traiangular-L and on the case that I called 
pure accuracy, other results of ALS, ALS-biases are not applied in this case}
We evaluate prediction methods using accuracy, sensitivity and specificity defined as follows:
\[
        Accuracy = \frac{TP+TN}{TP+TN+FP+FN}
\]
\[
        Sensitivity = \frac{TP}{TP+FN}
\]
\[
        Specificity = \frac{TN}{TN+FP}
\]
Where TP is the number of True Positives (correctly predicted errors), 
FP is the number of False Positives, TN is the number of true negatives 
and FN is the number of false negatives.

@@

\subsubsection{Random Unreal}
This method has a great performance with absolute accuracy of more than $0.95$ 
even by accessing to small training size of 10 percent. As it mentioned earlier 
this method is not applicable in pipline due to timestamp consideration but it 
is a good criterion to estimate the performance of other methods and try to modify 
the proposed methods in order to their accuracy be as closed as possible to the 
Random Unreal method ones.

\subsubsection{Complete Columns}
The Complete Columns method has almost a constant accuracy even if the training ratio increased and it
is almost two times less than dummy classifier in more differentiated
condition pairs (CentOS5 vs CentOS7 and CentOS6 vs CentOS7). But in the
best case which it means in similar conditions the Complete Columns
accuracy is as much accurate as the Dummy classifier is, $0.65$
percent.
\\
\subsubsection{Complete Rows}
This method has some flactuation over the gowth of training set size. These falactuations are more 
frequent in condition pairs which have higher difference positive ratio. 
Also by enlarging the training ratio specially between $0.3$ to $0.7$, 
we can see dummy classifier has better results than Complete Rows ones. 
In other words despite of better performance of Complete Rows than 
dummy classifier at the last 10 percent of the graph, its accuracies 
are less than dummy classifiers ones.  
\\
\subsubsection{Random Subjects-RS}
Same to the Complete Row method, RS method has some flactuation but not as frequent 
as Complete Rows method. Althogh there are some up and down trends specialy with 
training ratio range of $0.2$ to $0.6$ but its constant growth trend after 
training ratio $0.3$ in condition pairs with high difference positive ratio is considerable.
The method can be $0.99$ percent accurate when it has over 70 percent of the data however 
this accuracy can be achived with higher training ratio (over 80 percent) for C5C6.  
\\
\\
\noindent Figure~\ref{fig:ALS-Succeed} represents
the accuracy graph of all Random kind methods with comparision to dummy
classifier over the increasement of the training ratio.\\
\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs6}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-5vs7}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS/ALS-Succeed-6vs7}
        \end{subfigure}
        \caption{Average performance of RFNU methods in three different condition pairs}
        \label{fig:ALS-Succeed}
\end{figure}
\subsubsection{Random File Numbers(Uniform) - RFNU}
The continuous rise of RFNU accuracy trend can be observed in Figure~\ref{fig:ALS-Succeed}.
However a 0.03 drop is recorded in C6C7 between training ratio size of $0.8$ to $0.9$. 
This method takes over the dummy accuracy after having a training size more than 40 percent 
in condition pairs of C5vsC7 and C6vsC7 but it always shows better acuracy than 
dummy classifier ($0.73$ percent with traininfg ratio of $0.1$).\newline

% ALS-RFNT approaches
\indent As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.\newline

\subsubsection{RFNT-L}

In Figure~\ref{fig:ALS-Succeed}, the results show that RFNT-L performance is always more accurate than
dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
Dispite of this sudden, RFNT-L method has slight growing trend throughout the 
increment of training ratio and its accuracy is always more than $90\%$.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Adding biases}
In this part of the experiment, the effect of both subjects' and files' biases are considered in the predicted value. 
Our three random sampeling techniques are compered in Figure~\ref{fig:ALS-Bias-PFS} accross the accretion of training 
ratio;$\alpha$; and the results are reported at the following subsections.

@@

\subsubsection{RFNU}
The obtained results show that by sampling at least half of the utility matrix, 
the predicted accuracy would be as accurate as the baseline (Random Unreal technique) 
but for the $\alpha$ of less than $50\%$ this is not true. Actually there is a 
difference range of $0.2$ to $0.7$ between the accuracy of Random Unreal and RFNU techniques for
$\alpha <0.5$ in C5C7 and C6C7 but this range chanhe to $(0.07,0.17)$ in C5C6.

\subsubsection{RFNT-L}
As it mentioned earlier RFNT-L technique is applicable for $\alpha \leq \nicefrac{1}{3}$, therefore its 
accuracy description is summerized for $\alpha > 0.3$. This accuracy of this technique is always higher than 
dummy classifier. Results show that this RFNT-L reaches to $100\%$ accuracy by $\alpha >0.8$ in condition pairs
with more errors, however the baseline never reached this high accuracy throughout of whole experiment.

\subsubsection{RFNT-S}
This sampling technique is as precise as Random Unreal with maximum difference gap of 0.07 between them which that 
happend in C5C7 at $\alpha = 0.7$ with accuracy of $0.91$.
